full title

### 2020-11-21 paper/pldi21/abstract.tex
Removed inred

In this paper, we propose a novel technique to take advantage of the
high performance of dynamic analysis for JavaScript static analysis
in a sound way by using \textit{dynamic shortcuts}.  A dynamic shortcut
consists of three parts: 1) converting an abstract state to its corresponding
\textit{sealed symbolic state}, 2) performing \textit{sealed symbolic execution}
on the sealed symbolic state, and 3) converting a sealed symbolic state
to its corresponding abstract state. By taking dynamic shortcuts
during static analysis, we can significantly improve the analysis
scalability and precision by using highly-optimized commercial JavaScript engines
and lessen the modeling efforts by performing sealed symbolic execution for opaque code.
We formally define static analysis using dynamic shortcuts in the abstract
interpretation framework.  We actualize the technique via $\tool$, an
extended combination of SAFE and Jalangi, a static analyzer and a
dynamic analyzer, respectively.  We evaluated $\tool$ using
269 official tests of Lodash 4 library.
Our experiment shows that $\tool$ is \inred{6.30}x faster than the
baseline static analyzer, and it improves the precision to
detect 6 more dead branches on average by using sealed symbolic execution for
\inred{12} opaque functions.
\end{abstract}

>>>>

In this paper, we propose a novel technique to take advantage of the
high performance of dynamic analysis for JavaScript static analysis
in a sound way by using \textit{dynamic shortcuts}.  A dynamic shortcut
consists of three parts: 1) converting an abstract state to its corresponding
\textit{sealed symbolic state}, 2) performing \textit{sealed symbolic execution}
on the sealed symbolic state, and 3) converting a sealed symbolic state
to its corresponding abstract state. By taking dynamic shortcuts
during static analysis, we can significantly improve the analysis
scalability and precision by using highly-optimized commercial JavaScript engines
and lessen the modeling efforts by performing sealed symbolic execution for opaque code.
We formally define static analysis using dynamic shortcuts in the abstract
interpretation framework.  We actualize the technique via $\tool$, an
extended combination of SAFE and Jalangi, a static analyzer and a
dynamic analyzer, respectively.  We evaluated $\tool$ using
269 official tests of Lodash 4 library.
Our experiment shows that $\tool$ is 6.30$\x$ faster than the
baseline static analyzer, and it improves the precision to
detect 6 more dead branches on average by using sealed symbolic execution for
12 opaque functions.
\end{abstract}

### 2020-11-21 paper/pldi21/conclusion.tex
Removed inred

\section{Conclusion}\label{sec:conclusion}
We presented a novel technique for JavaScript static analysis using \textit{dynamic shortcuts}.
It can significantly accelerate static
analysis by freely leveraging high performance of dynamic analysis for
concretely executable program parts.  To maximize such benefits,
we proposed \textit{sealed symbolic execution}, which performs
concrete execution using sealed symbolic values for abstract values.
We formally defined static analysis using dynamic shortcuts in the
abstract interpretation framework and proved its soundness and termination.
We developed $\tool$ as a prototype implementation of the proposed approach
by extending a combination of the state-of-the-art static and dynamic
analyzers SAFE and Jalangi.  Our tool accelerates the speed
of static analysis \inred{19.96}x for original tests and \inred{6.30}x for
abstracted tests of Lodash 4 library.  Moreover, it detects \inred{6} more
dead branches by using sealed symbolic execution instead of
manual modeling for \inred{12} opaque functions on average.

>>>>

\section{Conclusion}\label{sec:conclusion}
We presented a novel technique for JavaScript static analysis using \textit{dynamic shortcuts}.
It can significantly accelerate static
analysis by freely leveraging high performance of dynamic analysis for
concretely executable program parts.  To maximize such benefits,
we proposed \textit{sealed symbolic execution}, which performs
concrete execution using sealed symbolic values for abstract values.
We formally defined static analysis using dynamic shortcuts in the
abstract interpretation framework and proved its soundness and termination.
We developed $\tool$ as a prototype implementation of the proposed approach
by extending a combination of the state-of-the-art static and dynamic
analyzers SAFE and Jalangi.  Our tool accelerates the speed
of static analysis 19.96$\x$ for original tests and 6.30$\x$ for
abstracted tests of Lodash 4 library.  Moreover, it detects 6 more
dead branches by using sealed symbolic execution instead of
manual modeling for 12 opaque functions on average.
